\TITLE

### 2023-11-08 paper/main.tex
improve fairness analysis

\section{Fairness analysis}\label{sec:fairness-analysis}
We analyse the fairness of the protocol by representing it as an interactive non-cooperative game.

\subsection{Model}\label{sec:fairness-model}
We consider three positions:

\begin{itemize}
\item \textbf{Neutral position ($\neutral{}$)}: when a party has neither spent nor gained anything of significant value (money, time, effort). For example, at the beginning of the protocol.
\item \textbf{Disadvantaged position ($\minus{}$)}: when a party has put a significant value without receiving an equivalent. For example, the customer has paid in advance for a service.
\item \textbf{Advantaged position ($\plus{}$)}: when a party would benefit if the transaction was stopped at this step. For example, the SP has received payment before the service has been provided.
\end{itemize}

There are many actions that each party can take, but we group them into two categories:

\item \textbf{Normal}: taking actions prescribed by the protocol.
\item \textbf{Abnormal}: anything that deviates from the intended steps of the protocol. For example, sending an arbitrary message, skipping or repeating steps, or timing out.
\end{enumerate}

In addition, at each step of the protocol, the customer can start a dispute, so another dimension with two positions must be taken into account:

\item \textbf{Agree}: the customer agrees with the action and therefore does not start a dispute.
\item \textbf{Start a dispute}: the customer disagrees with the action and therefore starts a dispute.
\end{enumerate}

As a result, in our analysis we need to consider four different outcomes for each party of the protocol ($\mathrm{party \in \{C, SP}\}$), for each step of the protocol ($\mathrm{step \in 1..9}$):

\item
  $\mathrm{\sigma_{step,party,n}}$: after following the protocol when the other party acted normally.
\item
  $\mathrm{\sigma_{step,party,d}}$: after a settled dispute when the other party acted normally.
\item
  $\mathrm{\sigma_{step,party,\overline{n}}}$: after not starting a dispute despite the other party has acted abnormally.
\item
  $\mathrm{\sigma_{step,party,\overline{d}}}$: after a settled dispute when the other party has acted abnormally.
\end{itemize}

The protocol terminates after the last step, after starting a dispute, or after a party fails to complete its designated action in time. Therefore, all positions except $\mathrm{\sigma_n}$ are termination positions.

Because the customer is anonymous, the SP cannot start a dispute - there is no way to identify the customer. To mitigate this problem, we designed the protocol so that the SP who follows the protocol is always in an advantageous position and therefore has no reason to start a dispute. On the other hand, the customer can start a dispute at any time during the protocol, but only the actual misbehaviour of the SP will make him win the conflict.

\begin{definition}[Fairness] \label{def:fairness}
A protocol achieves fairness iff 
\begin{equation*}
\begin{split}
\forall_{party \in parties}\forall_{\mathrm{step} \in \mathrm{steps}} &\operatorname{can\ move}\\
&\operatorname{to the\ non-disadvantaged\ position} 
\end{split}
\end{equation*}

@@

Below we list the assumptions we take for the analysis purpose.

\begin{enumerate}
\item Both parties start from a neutral position ($\neutral${}).
\item After completing a transaction, both parties end up in an advantageous position (\plus{}). In other words, they have an intrinsic motivation to initialise and complete the transaction.
\item The protocol steps are atomic - there are no intermediate steps.
\item The protocol can only go forward - there is no way to undo any action.
\item Repeating the first step starts a new transaction. Repeating any other step is considered abnormal and is ignored. For example, paying the invoice twice has no effect on the curse of the protocol.
\item Once published, the result is available to the customer on the storage network. 
\item Winning the dispute results in a neutral position ($\neutral${}).
\item Losing the dispute results in a penalty greater than any reward, leading to a disadvantaged position (\minus{}). Therefore, the rational customer will not start a dispute that he is not sure he can win.
\item Both the customer and the SP are rational. They always prefer to go from the worst position (\minus{} or $\neutral${}) to a better position ($\neutral${} or \plus), but they are willing to risk a temporary worst position in favour of a later better position if and only if they can always get out of the worst position; in particular, the customer can always start a dispute and, if the SP has misbehaved, get out of the disadvantaged position (\minus) to the neutral position ($\neutral${}).
\item We assume that the customer's materials without personal information are useless and the effort to deliver the package is negligible, so the customer's first step does not lead to a disadvantaged position.
\item We assume that the processing cost of publishing $\mathrm{PoD}$ is negligible and compensates for the customer's effort in delivering the package.
\end{enumerate}

@@

Figure~\ref{fig:positions} shows the positions of each party after each possible action taken.

\begin{figure}[h!]
\includegraphics[width=\linewidth]{model.png}
\centering
\caption{Visual representation of the fairness of the protocol. The figure shows the game-theoretic outcomes of each party after each possible actions taken. Symbol $\neutral${} represents neutral outcome, \minus{} represents disadvantaged outcome, and \plus{} represents advantaged outcome, where the order relation holds \minus{} < $\neutral${} < \plus{}.}
\label{fig:positions}
\end{figure}

The detailed description of each step and the rationale for the outcome is given in Appendix~\ref{app:proof-of-fairness}.

\subsection{Example scenarios}\label{example-scenarios}
The Figure~\ref{fig:misbehaviour} shows the transitions of positions when the SP tries to misbehave and does not perform the service and therefore does not publish $\mathrm{PoP}$ after receiving the payment. After the deadline $\mathrm{T}_\mathrm{provide}$ the SP cannot publish valid $\mathrm{PoP}$ and so the customer starts a dispute. The customer wins the dispute because the SP cannot prove that the $\mathrm{PoP}$ was published before $\mathrm{T}_\mathrm{provide}$. The protocol ends up neutral for the customer and disadvantageous for the SP's positions.

\begin{figure}[h!]
\includegraphics[width=\linewidth]{misbehaviour.png}
\centering
\caption{Transitions of positions where the SP is misbehaving and the customer starts a dispute.}
\label{fig:misbehaviour}
\end{figure}

The rational course for both parties is to follow the protocol shown in Figure~\ref{fig:rational}.

\begin{figure}[h!]
\includegraphics[width=\linewidth]{rational.png}
\centering
\caption{Transitions of positions where both the customer and the SP follow the protocol.}
\label{fig:rational}
\end{figure}

Using the definition of fairness~\ref{def:fairness} and the assumptions listed in Section~\ref{sec:assumptions}, our analysis shows that the protocol achieves fairness.

@@

\subsection*{Setup}

We have developed a prototype of our protocol using the following technologies:

\begin{itemize}
  \item{Anonymous Payments} - we use the Monero blockchain \cite{noetherRingSignatureConfidential2015}.
  \item{Storage Network} - we use the Powergate~\cite{textilePowergate2023}, which is a wrapper around Filecoin and IPFS.
  \item{Message Board} - we use the Ethereum blockchain~\cite{woodEthereumSecureDecentralised2014}; specifically, its local development version Truffle Ganache and the Solidity language.
\item{Customer and SP} - we create client-side web application (webapp) using \texttt{React.js} and \texttt{web3.js} library for interaction with Ethereum. We use \texttt{MetaMask} browser extension to sign and submit transactions to the Ethereum node. We use \texttt{monerod} network client and \texttt{monero-wallet-cli} command line interface to interact with the Monero blockchain.
\end{itemize}

@@

% The prototype is available at \url{https://anonser.stan.bar}. The source code is available at \url{https://github.com/stanbar/anonymous-provision-of-services-via-blockchain}.

We developed and tested our prototype in the following environment: OS — Arch Linux 5.11.8; Docker — 20.10.5; CPU — Intel(R) Core(TM) i7-4790 (8) 4.00~GHz; RAM — 16 GB DDR3; Storage — Samsung PM85 256~GB SSD; monerod and monero-wallet-cli — v0.18.1.2; Powergate — v2.6.2; Ganache — v7.5.0; Solidity — v0.8.17; ReactJS — v18.0.25; web3.js — v1.8.1; crypto-js — v4.1.1.

For simplicity, all components run on one, mentioned above, physical machine; and all processes are managed by Docker.

\subsection*{Preparation}

Both the customer and the SP create Monero wallets using the \texttt{monero-wallet-cli} command line tool.

The SP deploys the smart contract using the \texttt{truffle migrate --network development} command, which deploys the smart contract to the Ethereum blockchain. The web application is configured to use the last deployed smart contract address.

The customer receives some test Monero funds using the Faucet service available at \url{https://community.rino.io/faucet/stagenet/}.

Next, the customer enables per-transaction proof generation (payment \texttt{receipt}) by setting \texttt{set store-tx-info 1} for their wallet. This is required to verify the payment in the event of a dispute.

At this point both the customer and the SP are ready to start the protocol.

\subsection*{Experiment}

The customer and the SP are two different users of our prototype, but for simplicity, they use the same machine and the same web application.

The experiment was conducted as follows:

\begin{enumerate}
  \setcounter{enumi}{0}
  \item[0.] The protocol starts with the customer opening the webapp and creating a new provision.
The application generates a random ECDSA (secp256k1) customer keypair and a random 32-byte provisionID, and then displays a QR code that encodes both the provisionID and the customer's public key. 
The customer's private key must be downloaded and provided later to decrypt the results.

  \item[1.] The customer prints the QR code, sticks it on a parcel and delivers the parcel to the SP either via the SP's drop box, parcel locker services (e.g. Amazon Locker, InPost~\cite{inpostParcelLockerService}), the customer's trusted delivery agent or the post office.

  \item[2.1.] The SP opens the app and scans the QR code, which decodes the provisionID and the customer's public key.

  \item[2.2.] Since (in this experiment) the provision was not paid in cash, the SP generates a unique Monero payment address using \texttt{monero-wallet-cli integrated\_address}. 
  \item[2.3.] The SP submits the Proof of Delivery to the Ethereum blockchain using the MetaMask interface.

  % monero-wallet-cli --stagenet --wallet-file sp --password "" integrated_address
  % Random payment ID: <2b6d65d7d48b7896>
  % Matching integrated address: 5LHmrsVsQM2Q2TgqufX4A5gKPpxy1czHULDyVc84omvnh1nQLVmqXk4VBuy8WnX1AXfKxDx7xuASAc6svkZqGVkL1XkUBWT7QejHymEaYM
  \item[3.] The customer (using the webapp) checks the transaction status on the Ethereum blockchain by calling \texttt{getProvision} with arguments \texttt{customerPubKey} and \texttt{provisionID}.
  % monero-wallet-cli --stagenet --wallet-file customer --password "" transfer 5LHmrsVsQM2Q2TgqufX4A5gKPpxy1czHULDyVc84omvnh1nQLVmqXk4VBuy8WnX1AXfKxDx7xuASAc6svkZqGVkL1XkUBWT7QejHymEaYM 1
  % Transaction successfully submitted, transaction <7d89c04de458cfb76a811d5eb325075dec59f7a993c3bf7ce37f9e3a1630af65>
  % monero-wallet-cli --stagenet --wallet-file customer --password "" get_tx_key 7d89c04de458cfb76a811d5eb325075dec59f7a993c3bf7ce37f9e3a1630af65
  % Tx key: 1364dc848a752bf52011f4a63d98bcb16091cacd985713b6b5264b3ede6de40f

  \item[4.] The customer sends the payment (using \texttt{monero-wallet-cli transfer}) to the \texttt{paymentAddress} specified in the smart contract and stores the payment receipt (using \texttt{monero-wallet-cli get\_tex\_key <tx-id>}) in case of a dispute.
  \item[5.] Once the SP notices the payment on the Monero blockchain, it starts providing the service and outputs the file \texttt{result.pdf}.

  \item[6.] The SP uploads the file \texttt{result.pdf} to the IPFS and Filecoin networks using Powergate. As a result, the SP receives the content identifier \texttt{cid}, as well as \texttt{dealID} and \texttt{minerID}.

  \item[7.] The SP submits a Proof of Provision transaction to the Ethereum blockchain by calling \texttt{proofOfProvision} with arguments \texttt{customer\-PubKey}, \texttt{provisionID}, \texttt{cid} and \texttt{dealID}.

  \item[8.] Meanwhile, the customer subscribes to Ethereum and waits for the SP to publish the Proof of Provision.
 Once the Proof Of Provision is published, the customer downloads the result using either the IPFS network using \url{https://dweb.link/<cid>} or Lotus network using \texttt{lotus retrieve <cid> <minerID>}.

  \item[9.] The results are then decrypted using the customer's previously stored private key. If everything is correct, the customer is satisfied with the service and the protocol ends, otherwise the customer can initiate a dispute.

@@

\paragraph{Fairness}
Fairness within the protocol was demonstrated, as detailed in Section~\ref{sec:steps} and ~\ref{app:proof-of-fairness}. This was achieved through an undeniable handshake mechanism, where the SP first commits to the package delivery and service deadlines by publishing the PoD (as outlined in step 2). The customer then acknowledges this commitment and accepts the terms by proceeding with the payment for the service (step 3).

@@

\paragraph{Anonymity}
Anonymity was achieved through the decoupling of personal information from transactional elements such as materials, payment, and communication. Anonymous payment methods were employed, including cash and privacy-focused cryptocurrencies like Monero, which obscure the details of transactions. Decentralized storage networks, namely IPFS and Filecoin, were also utilized to enhance privacy. These networks enabled the storage and retrieval of information without the need to disclose the customer's identity, ensuring that customers could engage with the protocol anonymously at every stage.

@@

\subsection{Dispute Resolution Service}\label{sec:decentralised-justice}
Centralised Dispute Resolution Service is the biggest obstacle to the realisation of a system that is compliant with the Web3 postulates~\cite{ethereumWhatWeb3Why2023}.

Possible directions for mitigating such problems are either (i) replacing local justice with blockchain dispute resolution systems, such as those proposed in Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022, gudkovCrowdArbitrationBlockchain2020}, Aragon Court~\cite{aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}; or (ii) make it infeasible to provide incorrect results.

The first approach is more feasible in the near future. It would require the creation of a large set of experts in a field who, in the case of a dispute, would receive all the proofs ($\mathrm{PoD}$, $\mathrm{PoP}$, payment $\mathrm{receipt}$ as well as any other proofs relevant to the case) that could be queried by the experts in a zero-knowledge fashion, i.e. they could ask a limited number of questions of the proofs and get yes/no answers. The case would be completely confidential as they would not be able to query any personal information. Experts would be incentivised to participate in the pool by the fee system. They would be incentivised to vote honestly by the stake they would have to lock and the reward/punishment they would receive for a correct/incorrect judgement, correctness being determined by the quorum of votes.

The second is more futuristic. Let us assume that the service we are performing is fully computable. Then it would be possible to use proofs of correctness of computations~\cite{ben-sassonSNARKsVerifyingProgram2013} to enforce that only correct computations (and hence correct services) are accepted. This would require the entire service verification to be computable, which is difficult to achieve in settings where physical materials (such as blood) are examined. Specifically, the problem boils down to ``How to represent blood digitally?'' If we could represent urine, blood, saliva or any other physical material in a binary format and let the customer take a sample, discrete it and send it to the SP, then the whole chain of integrity could be ensured. This would make it impossible to provide the wrong service and therefore avoid disputes.

\subsection{Self-sovereign identities}
Our research in this area has shown that some jurisdictions require SPs to link the diagnosis to the customer's personal data. For example, in Poland, all laboratories performing medical diagnostic tests and collecting the material (except for HIV tests) are required to uniquely identify and verify the identity of the patient from whom the material was collected~\cite{ministerstwozdrowiaRegulationMinisterHealth2006}.

This conflicts with the main aim of our protocol, which is to prevent the collection of any identifying information.

A promising solution would be to use self-sovereign identities (SSIs)~\cite{muhleSurveyEssentialComponents2018}, especially the verifiable claims. A trusted authority (e.g. a government) would issue a one-time claim for the customer, which would be accepted by the SP as a legitimate personal identification. The SP would associate the diagnosis result with the provided DID. The DID itself would contain no personal information, so the SP would learn nothing about the customer's identity beyond the random-looking identification. The DID could be de-anonymised in cooperation with the government.

However, as SSI is a relatively new technology and the government has not yet adopted it, we decided to leave the discussion of this topic for future work.

\subsection{Formal Verification}\label{sec:formal-verification}
Following the work of~\cite{birjoveanuFormalVerificationMultiparty2022}, the security analysis of our protocol could be improved by using automatic formal verification tools, such as AVISPA~\cite{armandoAVISPAToolAutomated2005}. It would require the specification of the protocol using the High-Level Protocol Specification Language (HLPSL)~\cite{chevalierHighLevelProtocol2004}. The specification would then be translated into the AVISPA intermediate language and verified using the AVISPA theorem prover. The verification would be performed by the AVISPA model checker, which would check the protocol against the security properties.

\section{Conclusions}\label{sec:conclusion}
In this work, we have focused on enabling the provision of services without the collection of personal data. Our aim was to enable services such as genetic testing, testing for paternity, venereal diseases, HIV, drugs and steroids, or anonymous legal advice.

We found that the current state of the art was not sufficient to achieve this goal. We have therefore proposed a service delivery protocol that simultaneously achieves anonymity, fairness, dispute resolution, TTP-lessness and supports physical materials.

Payments are made in either cash or anonymous cryptocurrencies. The result of the service is published on a content-addressable p2p network. The dispute can be resolved by submitting the collected evidence to the dispute resolution service.

Using the Definition~\ref{def:fairness}, we showed that the protocol achieves fairness by publishing proof of delivery, proof of payment, and proof of provisioning on the message board.

Finally, we identified other improvements such as decentralised dispute resolution, self-sovereign identifiers, and anonymous courier delivery.

@@

\end{document}

>>>>

\section{Fairness Analysis}\label{sec:fairness-analysis}
Our protocol's fairness is assessed through its representation as an interactive non-cooperative game, examining the strategic interactions between the service provider (SP) and the customer.

\subsection{Model}\label{sec:fairness-model}
We define three distinct positions to represent the state of each party within the protocol:

\begin{itemize}
\item \textbf{Neutral Position ($\neutral{}$)}: A party's state when no significant resources (money, time, effort) have been expended or acquired.
\item \textbf{Disadvantaged Position ($\minus{}$)}: A party's state when it has invested resources without receiving a commensurate return, like a customer who has prepaid for a service.
\item \textbf{Advantaged position ($\plus{}$)}: A scenario where halting the transaction would result in a benefit for a party, for instance, if the SP has been paid but has not yet provided the service.
\end{itemize}

The actions of each party are categorized as follows:

\begin{enumerate}
\item \textbf{Normal}: Those that adhere to the protocol's prescribed steps.
\item \textbf{Abnormal}: Any deviation from the protocol's prescribed steps, such as sending irrelevant messages, skipping steps, or exceeding time limits.
\end{enumerate}

Additionally, the customer has the option to initiate a dispute at any protocol step, introducing another strategic layer:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item \textbf{Agree}: The customer consents to the action and refrains from disputing.
\item \textbf{Start a dispute}: The customer contests the action and initiates a dispute.
\end{enumerate}

Consequently, our analysis must account for four potential outcomes for each party at every protocol step ($\mathrm{party \in \{C, SP}\}$, $\mathrm{step \in 1..9}$):

\begin{itemize}
\item $\mathrm{\sigma_{step,party,n}}$: The outcome after adhering to the protocol with the other party acting normally.
\item $\mathrm{\sigma_{step,party,d}}$: The outcome following a resolved dispute with the other party acting normally.
\item $\mathrm{\sigma_{step,party,\overline{n}}}$: The outcome when no dispute is raised despite the other party's abnormal actions.
\item $\mathrm{\sigma_{step,party,\overline{d}}}$: The outcome after a resolved dispute with the other party acting abnormally.
\end{itemize}

The protocol concludes after the final step, if a dispute is initiated, or if a party fails to perform its required action within the designated timeframe. Hence, all positions except $\mathrm{\sigma_n}$ signify the end of the protocol.

The anonymity of the customer prevents the SP from initiating a dispute. To address this, the protocol is designed in such a way that an SP who adheres to the protocol remains in an advantageous position, eliminating the incentive to dispute. Conversely, the customer can dispute at any time, but only proven misbehavior of the SP will result in a successful dispute.

\begin{definition}[Fairness] \label{def:fairness}
A protocol is considered fair iff 
\begin{equation*}
\begin{split}
\forall_{party \in parties}\forall_{\mathrm{step} \in \mathrm{steps}} &\operatorname{can\ move}\\
&\operatorname{to\ the\ non-disadvantaged\ position} 
\end{split}
\end{equation*}

@@

For the purpose of our analysis, we operate under the following assumptions:

\begin{enumerate}
\item Both parties start from a neutral position ($\neutral{}$), implying no initial advantage or disadvantage.
\item Upon successful transaction completion, both parties attain an advantageous position (\plus{}), indicating mutual benefit and motivation to engage in and complete the transaction.
\item The steps within the protocol are atomic, meaning they are indivisible and have no intermediate states.
\item The protocol is unidirectional; actions taken cannot be reversed or undone.
\item The protocol can only be restarted by repeating the first step. Any repetition of subsequent steps is considered abnormal and will be disregarded. For example, a double payment does not change the course of the protocol.
\item Once the service result is published, it becomes accessible to the customer via the storage network.
\item A successful dispute resolution restores the disputing party to a neutral position ($\neutral{}$).
\item Losing a dispute incurs a penalty that exceeds any potential gain, resulting in a disadvantaged position (\minus{}). This discourages frivolous or uncertain disputes.
\item Both the customer and the SP are rational actors who prefer to move from a less advantageous to a more advantageous position. However, they may temporarily accept a less advantageous position if it leads to a subsequent advantageous state, as long as there is an escape route from the less advantageous position. Specifically, the client can initiate a dispute to move from a disadvantaged (\minus{}) to a neutral ($\neutral{}$) position if the SP fails to comply with the protocol.
\item The customer's materials, without personal information, have no value and the effort to deliver the package is considered minimal. Thus, the customer's first step does not lead to a disadvantaged position.
\item The cost of publishing the Proof of Delivery (PoD) is negligible and is offset by the customer's effort in delivering the package.
\end{enumerate}

@@

The fairness of our protocol is visually represented in Figure~\ref{fig:positions}, which illustrates the positions of each party following each possible action within the protocol.

\begin{figure}[h!]
\includegraphics[width=\linewidth]{model.png}
\centering
\caption{Visual representation of the fairness of the protocol. This figure shows the outcomes for each party after various actions. The symbols used are $\neutral{}$ for a neutral outcome, \minus{} for a disadvantaged outcome, and \plus{} for an advantaged outcome. The order relation is defined as \minus{} < $\neutral{}$ < \plus{}.}
\label{fig:positions}
\end{figure}

The detailed description of each step and the reasoning for the outcomes is given in~\ref{app:proof-of-fairness}.

\subsection{Example scenarios}\label{example-scenarios}
This section illustrates two key scenarios using figures to demonstrate the transitions of positions between the customer and the SP under different conditions.

\begin{figure}[h!]
\includegraphics[width=\linewidth]{misbehaviour.png}
\centering
\caption{Transitions of positions in a scenario where the SP misbehaves by not performing the service and failing to publish $\mathrm{PoP}$ after receiving payment. This leads to the customer initiating a dispute.}
\label{fig:misbehaviour}
\end{figure}

In the first scenario (Figure~\ref{fig:misbehaviour}), the SP attempts to misbehave by not delivering the service and consequently not publishing the Proof of Provision ($\mathrm{PoP}$) after receiving payment. If the SP fails to publish a valid $\mathrm{PoP}$ by the deadline $\mathrm{T}_\mathrm{provide}$, the customer is justified in starting a dispute. The customer is likely to win this dispute as the SP cannot prove the timely publication of $\mathrm{PoP}$. This scenario results in a neutral outcome for the customer and a disadvantageous outcome for the SP.

\begin{figure}[h!]
\includegraphics[width=\linewidth]{rational.png}
\centering
\caption{Transitions of positions in a scenario where both the customer and the SP adhere to the protocol.}
\label{fig:rational}
\end{figure}

The second scenario (Figure~\ref{fig:rational}) represents the rational and intended course of action, where both the customer and the SP follow the protocol as designed. This scenario is crucial as it demonstrates the protocol functioning optimally, leading to a fair outcome for both parties.

By applying the definition of fairness from Section~\ref{def:fairness} and considering the assumptions outlined in Section~\ref{sec:assumptions}, our analysis confirms that the protocol achieves fairness under these scenarios (see ~\ref{app:proof-of-fairness} for detailed description).

@@

\subsection*{Setup, Preparation, and Experiment}

Our protocol's prototype was developed using a suite of technologies designed to ensure anonymity and security:

\begin{itemize}
  \item \textbf{Anonymous Payments:} Utilization of the Monero blockchain for secure transactions.
  \item \textbf{Storage Network:} Powergate serves as an interface for Filecoin and IPFS, facilitating decentralized storage.
  \item \textbf{Message Board:} The Ethereum blockchain, accessed via a local development version Truffle Ganache and Solidity, acts as a public ledger.
  \item \textbf{Customer and SP Interface:} A client-side web application built with \texttt{React.js} and \texttt{web3.js}, with \texttt{MetaMask} for Ethereum transactions and \texttt{monero-wallet-cli} for Monero interactions.
\end{itemize}

We used the following tools to create the experiment:
\texttt{monerod} and \texttt{monero-wallet-cli} - v0.18.1.2; \texttt{Powergate} - v2.6.2; \texttt{Ganache} - v7.5.0; \texttt{Solidity} - v0.8.17; \texttt{ReactJS} - v18.0.25; \texttt{web3.js} - v1.8.1; \texttt{crypto-js} - v4.1.1.

For simplicity, all components run on one physical machine; and all processes are managed by Docker.

@@

In preparation for the experiment, both the customer and the SP set up their Monero wallets using the \texttt{monero-wallet-cli}. The SP deploys the smart contract to the Ethereum blockchain with the \texttt{truffle migrate --network development} command, and the web application is then configured to interact with this newly deployed contract.

The customer acquires test Monero funds from a Faucet service and configures their wallet to generate transaction proofs, essential for dispute resolution.

With preparations complete, the experiment proceeds as follows:

\begin{enumerate}
  \item The customer begins by creating a new provision in the webapp, which generates a unique ECDSA keypair and provisionID. The corresponding QR code is printed and attached to the parcel for delivery.

  \item The parcel is delivered to the SP through a chosen delivery method, such as a secure drop box or locker service.

  \item Upon receipt, the SP scans the QR code to retrieve the provisionID and customer's public key.

  \item Since (in this experiment) the provision was not paid in cash, the SP generates a unique Monero payment address using \texttt{monero-wallet-cli integrated\_address}.

  \item The SP submits the PoD to the Ethereum blockchain using the MetaMask interface.

    \item The customer checks the transaction status on the Ethereum blockchain by calling \texttt{getProvision} with arguments \texttt{customerPubKey} and \texttt{provisionID}

    \item The customer sends the payment (using \texttt{monero-wallet-cli transfer}) to the \texttt{paymentAddress} specified in the smart contract and stores the payment receipt using \texttt{monero-wallet-cli get\_tex\_key <tx-id>}.

    \item Upon payment confirmation, the SP provides the service, resulting in a \texttt{result.pdf} file.

  \item This file is uploaded to IPFS and Filecoin, granting the SP a \texttt{cid}, \texttt{dealID}, and \texttt{minerID}.

  \item A PoP is submitted to the Ethereum blockchain by the SP.

    \item Meanwhile, the customer subscribes to Ethereum and waits for the SP to publish the PoP.
Upon noticing the PoP, the customer retrieves the result using either one of the public gateways\footnote{IPFS Public Gateway Checker, \url{https://ipfs.github.io/public-gateway-checker/}, (last visited Jan. 04, 2023)} like \url{https://cf-ipfs.com/ipfs/<cid>} or Lotus network using \texttt{lotus} \texttt{retrieve} \texttt{<cid>} \texttt{<minerID>}.

  \item The results are then decrypted using the customer's previously stored private key. If the customer is satisfied with the service the protocol ends; otherwise, the customer may initiate a dispute process.

@@

\paragraph{Fairness}
As shown in Section~\ref{sec:steps} and ~\ref{app:proof-of-fairness}, the protocol is fair. This was achieved through an undeniable handshake mechanism, where the SP first commits to the package delivery and service deadlines by publishing the PoD (as outlined in step 2). The customer then acknowledges this commitment and accepts the terms by proceeding with the payment for the service (step 3).

@@

\paragraph{Anonymity}
Anonymity was secured by breaking the link between personal data and transactional elements, including materials, payments, and communications. We utilized anonymous payment methods such as cash and privacy-centric cryptocurrencies like Monero, to conceal transactional details. Furthermore, we leveraged decentralized storage networks like IPFS and Filecoin, which facilitate the anonymous storage and retrieval of data. This approach guaranteed that customer interactions with the protocol remained confidential at every stage.

@@

\subsection{Dispute Resolution Service}\label{sec:decentralised-justice}
The central challenge in achieving a Web3-compliant system lies in the centralization of dispute resolution services~\cite{ethereumWhatWeb3Why2023}. To address this, we consider two potential solutions: the integration of blockchain-based dispute resolution systems and the development of mechanisms to ensure the infeasibility of incorrect service provision.

Blockchain-based dispute resolution platforms such as Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022, gudkovCrowdArbitrationBlockchain2020}, Aragon Court~\cite{aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B}, and other Online Dispute Resolution (ODR) systems~\cite{allenGovernanceBlockchainDispute2019} offer a promising direction. These systems could employ a pool of field experts who, in the event of a dispute, would examine the proofs (e.g., $\mathrm{PoD}$, $\mathrm{PoP}$, payment $\mathrm{receipt}$) in a confidential, zero-knowledge context, providing verdicts without access to personal data. Expert participation and honest adjudication would be encouraged through a system of fees, stakes, and rewards.

The second, more visionary approach involves ensuring service correctness through computational proofs, such as zkSNARKs~\cite{ben-sassonSNARKsVerifyingProgram2013}, which could validate the accuracy of services that are fully computable. This method, however, faces significant challenges in representing physical materials like blood or saliva digitally—a prerequisite for end-to-end service verification and the elimination of disputes.

\subsection{Self-sovereign Identities}
In our exploration of privacy-preserving protocols, we encountered regulatory requirements that mandate the linking of diagnostic results to patient identities, as is the case in Poland~\cite{ministerstwozdrowiaRegulationMinisterHealth2006}. Such regulations present a direct challenge to our protocol's objective of anonymity.

The concept of self-sovereign identities (SSIs) and verifiable claims offers a potential resolution~\cite{muhleSurveyEssentialComponents2018}. Under this system, a trusted entity, such as a government body, could issue a one-time, verifiable claim to the customer. Service providers would accept this claim as valid identification, linking diagnostic results to a Decentralized Identifier (DID) that holds no personal data. While this ensures the SP cannot deduce the customer's identity, the DID could be traced back to the individual by the issuing authority if necessary.

Given the early stage of SSI technology and its current lack of governmental adoption, we recognize the need for further research and development in this area.

\subsection{Formal Verification}\label{sec:formal-verification}
Following the work of~\cite{birjoveanuFormalVerificationMultiparty2022}, the security analysis of our protocol could be improved by using automatic formal verification tools, such as AVISPA~\cite{armandoAVISPAToolAutomated2005}. This process would involve formulating the protocol in the High-Level Protocol Specification Language (HLPSL)~\cite{chevalierHighLevelProtocol2004}, followed by its translation into AVISPA's intermediate format. Subsequently, AVISPA's tools would rigorously assess the protocol's adherence to established security properties through automated theorem proving and model checking techniques.

\section{Conclusions}\label{sec:conclusion}

This study has been dedicated to the development of a protocol that facilitates the provision of services while preserving the anonymity of the user. Our protocol is particularly applicable to services requiring a high degree of confidentiality, such as genetic testing, paternity determination, and anonymous legal consultation.

We found that the current state of the art was not sufficient to achieve this goal, so we have designed and implemented a novel protocol that ensures user anonymity, fairness in service delivery, and a mechanism for dispute resolution without the need for a trusted third party. This protocol leverages anonymous payment systems, such as cash or privacy-focused cryptocurrencies, and utilizes peer-to-peer networks for the dissemination of service results.

Through rigorous definition and analysis, we have demonstrated that our protocol meets the criteria for fairness, as outlined in Definition~\ref{def:fairness}. It does so by systematically publishing proofs of delivery, payment, and provisioning, ensuring a transparent and equitable process for all parties involved.

In closing, we have pinpointed several avenues for future enhancement, including the integration of decentralized dispute resolution systems, the application of self-sovereign identity (SSI) frameworks, and the exploration of anonymous physical delivery methods. These areas present exciting opportunities for further research and development towards the realization of fully anonymous service provision in the digital age.

@@
